\documentclass{article}
\usepackage{ctex}
\usepackage{multicol}
\usepackage[top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}
\usepackage{lscape}
\author{Zhang, Liqiang}
\date{April 15,2018}
\title{Privacy}

\begin{document}

\maketitle

It has become hotter and hotter about Facebook revealing user's privacy. Even if Zuckerberg has already apologized, but foreign netizens still want to address Facebook.As a matter of fact, it seems to be a open secret to leak user's privacy at the information companies in the era of big data.

At the China Development High-Level Forum on March 26, Li Yanhong, CEO of Baidu, said that Chinese people are willing to exchange privacy for convenience and they enjoy this very much. What? Uh, I think I may be a fake Chinese, the logic of an overbearing president is really overbearing. Actually, it should be not accidental: as a Chinese, we have been represented many times. These just like parents tell us they are for us after we found that they peeked our diary at childhood. Now, these APP , such as shopping, taxi and takeaway, become our "parents" which peep our chat history, camera and address book and tell us that they do this is to make us be more convenient. For example, If you search for what to do for arm pain in Baidu you will find that lots of APP recommend to you orthopaedic hospital.

Of course, being in the era of big data still benefits our users. It's OK to see the diaries of the "babies", because we have no way to select. As long as these "parents" do not read out and sell the diaries, those babies will be extremely excited.

\end{document}
