\documentclass{article}
\usepackage{ctex}
\usepackage{multicol}
\usepackage[top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}
\usepackage{lscape}
\author{Zhangliqiang}
\date{April 13,2018}
\title{Automatic driving}

\begin{document}

\maketitle

With the development of technology, automatic driving has become a technology pursued by some major automotive manufacturers. Tesla has been known for autonomous driving and it did achieve a lot of results, Tesla is the best in the world of automatic driving cars. And more importantly, it is mass-produced car, witch can't be produced by the other auto company.

But,a few days ago, a shocking cash has taken place in Mountain View, Calif. That killed Walter Huang, an Apple engineer whose Tesla electric SUV was on Autopilot mode. In the past ten years, Tesla chief executive Elon Musk has been trying to convince the car-buying masses that it is okay to entrust our lives to a hodgepodge of sensors and algorithms. But now, Tesla have to admit that its technology is still at the initial stage and because no technology is perfect, people in even the most advanced cars still has possibilities of cash. In fact, so-called automatic driving is the semi-automatic, the driver must take over the car if auto system can't handle some happenings. In the past few years, there have also been several accidents in China caused by Tesla's automatic driving. Well, is automatic driving really safe?

In my opinion, the machine can't be matched with human in many aspects, at least right now. There are a lot of unexpected circumstances, we haven't developed the CPU which can handle so many information in such a short time and to give right order to the car. So, automatic driving still have a long way to go.

\end{document}


