\documentclass{article}
\usepackage{ctex}
\usepackage{multicol}
\usepackage[top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}
\usepackage{lscape}
\author{Zhangliqiang}
\date{April 11,2018}
\title{The trade war II}

\begin{document}

\maketitle

With the escalation of the trade war,the stock market has also been greatly affected.In my memory, This is the first time that China counter U.S in the economic when United States take actions to limit Chinese economy developments. This shows that China has enough strength to establish itself in the world and to fight with the United States in certain aspects. 

When the Trump administration has threatened to impose tariffs on 150 billion dollars in Chinese imports over allegations of unfair trade practices, Chinese government also imposes 50 billion dollars tariff on American imports, especially in vehicles. I am interested in cars so I learn about that the U.S. vehicles account for 22 percent of the total number of imported cars in China, so this policy will definitely have a great impact on the U.S. automotive industry. But at the same time, China's auto industry will also be affected because many of China's automobile core components are imported from the United States such as transmission system, body accessories and engine parts which is great important for the auto.

All in all, the impact of Sino-US trade war will eventually make both sides hurt, no matter who suffers more damage from China and the United States. From many major news networks, most people believe that the Sino-US trade war is unlikely to start. But everything is possible, if Trump insists his idea,I believe that China will take the same actions to counter the United States.

\end{document}


